The Heavy Photon Search Test Detector

### 2013-11-06 hps-testrun-nim.tex
Adding turn-on vs E from Sho.

To eliminate trigger bias in checking the trigger decision, we use a tag and probe method. To check trigger 
performance in one half of the ECal, we tag events where there was a trigger in the other half, and exactly one 
probe cluster in the ECal half under test. 
We then measure trigger efficiency (proportion of tagged events where there was a trigger) as a function of 
ADC counts and energy of the probe cluster.
These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}. 
\begin{figure}[ht]
\begin{center}
{\small
	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag}
	\caption{Trigger turn-on as a function of probe cluster ADC counts. }
%	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
%	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
%	fraction.}
\label{fig:turnon}
}
\end{center}
\end{figure}
The trigger threshold is seen to be 1280 ADC counts as expected. The threshold is not perfectly sharp in this 
analysis because of uncertainties in the conversion from readout to trigger hits but based on comparisons 
with Monte Carlo simulation we believe the trigger worked exactly as specified. 
The trigger threshold in terms of cluster energy is very uneven for two reasons; gain variations between 
different ECal crystals lead to threshold variations and the nonlinearity of the time-over-threshold integral 
means that the effective threshold is higher for clusters that span multiple crystals.
Overall the trigger appears to have functioned exactly as intended. Changes planned for the next run 
(constant integration window and per-crystal gain calibration constants for the trigger) will solve both of the 
issues that led to threshold variations in the test run.

>>>>

To eliminate trigger bias in checking the trigger decision, we use a tag and probe method. To check trigger 
performance in one half of the ECal, we tag events where there was a trigger in the other half, and exactly one 
probe cluster in the ECal half under test. 
We then measure trigger efficiency (proportion of tagged events where there was a trigger) as a function of 
ADC counts and energy of the probe cluster.
These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}. 
\begin{figure}[ht]
\begin{center}
{\small
	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag}
	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag_E}
	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
	fraction.}
\label{fig:turnon}
}
\end{center}
\end{figure}
The trigger threshold is seen to be 1280 ADC counts as expected. The threshold is not perfectly sharp in this 
analysis because of uncertainties in the conversion from readout to trigger hits but based on comparisons 
with Monte Carlo simulation we believe the trigger worked exactly as specified. 
The trigger threshold in terms of cluster energy is very uneven for two reasons; gain variations between 
different ECal crystals lead to threshold variations and the nonlinearity of the time-over-threshold integral 
means that the effective threshold is higher for clusters that span multiple crystals.
Overall the trigger appears to have functioned exactly as intended. Changes planned for the next run 
(constant integration window and per-crystal gain calibration constants for the trigger) will solve both of the 
issues that led to threshold variations in the test run.
